Proof-Reconstruction in Type Theory for Propositional Logic

### 2017-10-23 paper/sections/proof-reconstruction/resolve.tex
last changes in subsections.

\begin{equation*}
 \label{eq:build-or}
  \begin{aligned}
  &\hspace{.495mm}\rm{build}_{∨} : \Prop → \Prop → \Prop\\
  &\begin{array}{llll}
    \rm{build}_{∨}&ψ~ψ &= ψ\\
    \rm{build}_{∨}&(φ~(ψ₁ ∨ ψ₂)&=ψ &\text{ if }\rm{build}_{∨}~φ~ψ_{1} ≡ ψ_{1}\\
    \rm{build}_{∨}&(φ~(ψ₁ ∨ ψ₂)&=ψ &\text{ if }\rm{build}_{∨}~φ~ψ_{2} ≡ ψ_{2}\\
    \rm{build}_{∨}&φ~ψ&=φ&\text{ otherwise.}
   \end{array}
  \end{aligned}
\end{equation*}

@@

\begin{mainlemma}[lem-build$_{\boldsymbol{∨}}$]
\label{lem:build-or}
  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \rm{build}_{∨}~φ~ψ$.
\end{mainlemma}

@@

\begin{align}
\begin{split}
  \label{eq:factor-definition}
  &\ffactor : \Prop → \Prop\\
  &\ffactor(φ) =
  \begin{cases}
    φ₁,  &\text{ if }φ ≡ φ₁ ∨ φ₂ \text{ and } φ₁ ≡ \ffactor(φ₂)\\
    φ,   &\text{ otherwise.}
  \end{cases}
\end{split}
\end{align}

\begin{mainlemma}[lem-factor]
\label{lem:factor}
  $Γ ⊢ φ$ then $Γ ⊢ \ffactor(φ)$.
\end{mainlemma}

To construct a disjunction $ψ$ from a disjunction $φ$, we have used ideas
from the description in \citeauthor{bohme2010}~\cite{bohme2010} to prove
equality between nested disjunctions.
We define the $\rm{sbuild}_{∨}$ function in
Eq.~(\ref{eq:strong-build-or-definition}).
that uses every disjunct from the source formula, $φ$, to build up the
target disjunction $ψ$.

\begin{align}
  \begin{split}
  \label{eq:strong-build-or-definition}
    &\rm{sbuild}_{∨} : \Prop → \Prop → \Prop\\
    &\rm{sbuild}_{∨}(φ, ψ) =%\\
    % &\hspace{3mm}
    \begin{cases}
      \ffactor(\rm{build}_{∨}(φ₁, ψ) ∨ \rm{build}_{∨}(φ₂,ψ)),
      &\text{ if }φ≡ φ₁ ∨ φ₂\\
      \rm{build}_{∨}(φ, ψ),  & \text{ otherwise.}
    \end{cases}
  \end{split}
\end{align}

\begin{mainlemma}
\label{lem:sbuild-or}
If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \rm{sbuild}_{∨}(φ, ψ)$.
\end{mainlemma}

@@

\begin{definition}[reorder$_{\boldsymbol{∧}}$]
  \begin{align*}
      \begin{split}
        &\freorder_{∧} : \Prop → \Prop \to \Prop\\
        &\freorder_{∧}(φ, ψ) =
        \begin{cases}
          φ, &\text{ if }φ ≡ ψ\\
          ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }\freorder_{∧}(φ, ψ₁) ≡ ψ₁\\
                  &\text{and }\freorder_{∧}(φ, ψ₂)≡ ψ₂\\
          φ,       &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
          \fconjunct(φ, ψ), &\text{ otherwise.}
        \end{cases}
      \end{split}
  \end{align*}
\end{definition}

\begin{mainlemma}
  \label{lem:reorder-and}
  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧}(φ, ψ)$.
\end{mainlemma}

\begin{definition}[conjunct$_{\boldsymbol{∨}}$]
  \label{eq:conjunct-or-definition}
\begin{align*}
  \begin{split}
    &\fconjunct_{∨} : \Prop → \Prop \to \Prop\\
    &\fconjunct_{∨}(φ, ψ) =
    \begin{cases}
      ψ, &\text{ if }φ ≡ ψ\\
      ψ, &\text{ if }\freorder_{∨}(φ, ψ) ≡ ψ\\
      ψ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂,\ \fconjunct_{∨}(φ, ψ₁) ≡ ψ₁,\\
        &\text{and } \freorder_{∨}(φ, ψ₂) ≡ ψ₂\\
      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ \fconjunct_{∨}(φ₁, ψ) ≡ ψ\\
      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ \fconjunct_{∨}(φ₂, ψ) ≡ ψ\\
      φ, &\text{ otherwise.}
    \end{cases}
  \end{split}
  \end{align*}
\end{definition}

\begin{mainlemma}
  \label{lem:conjunct-or}
  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fconjunct_{∨}(φ, ψ)$.
\end{mainlemma}

\begin{mainlemma}
  \label{lem:reorder-and-or}
  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}(φ, ψ)$, where
   \begin{align*}
      \begin{split}
      &\freorder : \Prop \to \Prop \to \Prop\\
      &\freorder_{∧∨}~φ~ψ~=
        \begin{cases}
          ψ, &\text{ if } φ≡ψ\\
          ψ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂,\ ψ₁ ≡ \freorder_{∧∨}~φ~ψ₁~\\
             &\text{and } ψ₂ ≡ \freorder_{∧∨}~φ~ψ₂~\\
          φ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂\\
          \fconjunct_{∨}~φ~ψ~ &\text{ otherwise.}
        \end{cases}
      \end{split}
  \end{align*}
\end{mainlemma}

>>>>

\begin{equation*}
 \label{eq:build-or}
  \begin{aligned}
  &\hspace{.495mm}\rm{build}_{∨} : \Prop → \Prop → \Prop\\
  &\begin{array}{llll}
    \rm{build}_{∨}&ψ~ψ &= ψ\\
    \rm{build}_{∨}&φ~(ψ₁ ∨ ψ₂)&=ψ &\text{ if }\rm{build}_{∨}~φ~ψ_{1} ≡ ψ_{1}\\
    \rm{build}_{∨}&φ~(ψ₁ ∨ ψ₂)&=ψ &\text{ if }\rm{build}_{∨}~φ~ψ_{2} ≡ ψ_{2}\\
    \rm{build}_{∨}&φ~ψ&=φ&\text{ otherwise.}
   \end{array}
  \end{aligned}
\end{equation*}

@@

\begin{mainlemma}
\label{lem:build-or}
  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \rm{build}_{∨}~φ~ψ$.
\end{mainlemma}

@@

\begin{mainlemma}
\label{lem:factor}
  $Γ ⊢ φ$ then $Γ ⊢ \ffactor~φ$, where, 
  \begin{equation}
  \label{eq:factor-definition}
   \begin{aligned}
   &\hspace{.495mm}\ffactor : \Prop → \Prop\\
    &\begin{array}{llll}
     \ffactor&(φ₁ ∨ φ₂) &=φ₁,  &\text{ if } φ₁ ≡ \ffactor~φ₂\\
     \ffactor&φ &= φ, &\text{ otherwise.}
  \end{array}
\end{aligned}
\end{equation}
\end{mainlemma}

To construct a disjunction $ψ$ from a disjunction $φ$, we have used ideas
from the description in \citeauthor{bohme2010}~\cite{bohme2010} to prove
equality between nested disjunctions.
We define the $\rm{sbuild}_{∨}$ function in
Eq.~(\ref{eq:strong-build-or}).
that uses every disjunct from the source formula, $φ$, to build up the
target disjunction $ψ$.

\begin{mainlemma}
\label{lem:sbuild-or}
If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \rm{sbuild}_{∨}~φ~ψ$, where, 
\begin{equation}
\label{eq:strong-build-or}
 \begin{aligned}
     &\hspace{.495mm}\rm{sbuild}_{∨} : \Prop → \Prop → \Prop\\
    &\begin{array}{llll}
    \rm{sbuild}_{∨}&(φ₁ ∨ φ₂)~ψ &=\ffactor(\rm{build}_{∨}~φ₁~ψ ∨ \rm{build}_{∨}~φ₂~ψ)&\\
    \rm{build}_{∨}&φ~ψ &= \rm{build}_{∨}~φ~ψ& \text{ otherwise.}
     \end{array}
\end{aligned}
\end{equation}
\end{mainlemma}

@@

\begin{definition}[reorder$_{\boldsymbol{∧}}$]
  \begin{align*}
      \begin{split}
        &\freorder_{∧} : \Prop → \Prop \to \Prop\\
        &\freorder_{∧}~φ~ψ =
        \begin{cases}
          φ, &\text{ if }φ ≡ ψ\\
          ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }\freorder_{∧}~φ~ψ₁ ≡ ψ₁\\
                  &\text{and }\freorder_{∧}~φ~ψ₂≡ ψ₂\\
          φ,       &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
          \fconjunct~φ~ψ, &\text{ otherwise.}
        \end{cases}
      \end{split}
  \end{align*}
\end{definition}

\begin{mainlemma}
  \label{lem:reorder-and}
  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧}~φ~ψ$.
\end{mainlemma}

\begin{definition}[conjunct$_{\boldsymbol{∨}}$]
  \label{eq:conjunct-or-definition}
\begin{align*}
  \begin{split}
    &\fconjunct_{∨} : \Prop → \Prop \to \Prop\\
    &\fconjunct_{∨}~φ~ψ =
    \begin{cases}
      ψ, &\text{ if }φ ≡ ψ\\
      ψ, &\text{ if }\freorder_{∨}~φ~ψ ≡ ψ\\
      ψ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂,\ \fconjunct_{∨}~φ~ψ₁ ≡ ψ₁,\\
        &\text{and } \freorder_{∨}~φ~ψ₂ ≡ ψ₂\\
      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ \fconjunct_{∨}~φ₁~ψ ≡ ψ\\
      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ \fconjunct_{∨}~φ₂~ψ ≡ ψ\\
      φ, &\text{ otherwise.}
    \end{cases}
  \end{split}
  \end{align*}
\end{definition}

\begin{mainlemma}
  \label{lem:conjunct-or}
  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fconjunct_{∨}~φ~ψ$.
\end{mainlemma}

\begin{mainlemma}
  \label{lem:reorder-and-or}
  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}~φ~ψ$, where
   \begin{align*}
      \begin{split}
      &\freorder_{∧∨} : \Prop \to \Prop \to \Prop\\
      &\freorder_{∧∨}~φ~ψ~=
        \begin{cases}
          ψ, &\text{ if } φ≡ψ\\
          ψ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂,\ ψ₁ ≡ \freorder_{∧∨}~φ~ψ₁~\\
             &\text{and } ψ₂ ≡ \freorder_{∧∨}~φ~ψ₂~\\
          φ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂\\
          \fconjunct_{∨}~φ~ψ~ &\text{ otherwise.}
        \end{cases}
      \end{split}
  \end{align*}
\end{mainlemma}
